---
output:
  github_document:
    html_preview: false
---

# hms

[![Travis-CI Build Status](https://travis-ci.org/tidyverse/hms.svg?branch=master)](https://travis-ci.org/tidyverse/hms)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/tidyverse/hms?branch=master&svg=true)](https://ci.appveyor.com/project/tidyverse/hms)
[![codecov](https://codecov.io/gh/tidyverse/hms/branch/master/graph/badge.svg)](https://codecov.io/gh/tidyverse/hms)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/hms)](https://cran.r-project.org/package=hms)

A simple class for storing durations or time-of-day values and displaying them in the hh:mm:ss format.
Intended to simplify data exchange with databases, spreadsheets, and other data sources.

The values are stored as a numeric vector that contains the number of seconds
since midnight.  Supports construction from time values, coercion to and from
various data types, and formatting, based on the `difftime` class.  Can be
used in a data frame.

Compared to `POSIXct`, no date is stored, although the values can exceed
the 24-hour boundary or be negative.
By default, fractional seconds up to a microsecond are displayed.

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{r}
library(hms)
hms(56, 34, 12)
as.hms(1)
as.hms("12:34:56")
as.hms(Sys.time())
as.POSIXct(hms(1))

data.frame(hours = 1:3, hms = hms(hours = 1:3))
```

Install the package from GitHub:

```r
# install.packages("devtools")
devtools::install_github("tidyverse/hms")
```
